Compositional Certified Resource Bounds\ifshort{\vspace{-1.15cm}}{}

### 2014-11-13 paper/main.tex
some small updates in related work

Our work has been inspired by type-based amortized resource analysis
for functional programs~\cite{Jost03,HoffmannH10,HoffmannAH12}.  Here,
we present the first automatic amortized resource analysis for
C. None of the existing techniques can handle the example programs we
describe in this work.
%
The automatic analysis of realistic C programs is enabled by three
major improvements over previous work.  First, we extended the
analysis system to associate potential with not just individual
program variables but also multivariate intervals
and, more generally, auxiliary variables.  Second, we solved the
long-standing open problem of extending automatic amortized resource
analysis to compute bounds for programs that loop on (possibly
negative) integers without decreasing one individual number in each
iteration.  Third, for the first time, we have combined an automatic
amortized analysis with a system for interactively deriving bounds. In
particular, recent systems~\cite{HoffmannS13} that deal with integers
and arrays cannot derive bounds that depend on values in mutable
locations, possibly negative integers, or on differences between
integers.

A recent project~\cite{veristack14} has implemented and verified a
quantitative logic to reason about stack-space usage, and modified the
verified CompCert C compiler to translate C level bound to x86 stack
bounds.  This quantitative logic is also based on the potential method
but has very rudimentary support for automation. It is not based on
efficient LP solving so it cannot automatically derive symbolic
bounds.  In contrast, our main contribution is an automatic amortized
analysis for C that can derive parametric bounds for loops and
recursive functions fully automatically.
%
In this article, we also use a more general quantitative Hoare
logic that is parametric in the resource of interest.

>>>>

Our work has been inspired by type-based amortized resource analysis
for functional programs~\cite{Jost03,HoffmannH10,HoffmannAH12}.  Here,
we present the first automatic amortized resource analysis for
C. None of the existing techniques can handle the example programs we
describe in this work.
%
The automatic analysis of realistic C programs is enabled by two
major improvements over previous work.  First, we extended the
analysis system to associate potential with not just individual
program variables but also multivariate intervals
and, more generally, auxiliary variables.  In this way, we solved the
long-standing open problem of extending automatic amortized resource
analysis to compute bounds for programs that loop on (possibly
negative) integers without decreasing one individual number in each
iteration.  Second, for the first time, we have combined an automatic
amortized analysis with a system for interactively deriving bounds. In
particular, recent systems~\cite{HoffmannS13} that deal with integers
and arrays cannot derive bounds that depend on values in mutable
locations, possibly negative integers, or on differences between
integers.

A recent project~\cite{veristack14} has implemented and verified a
quantitative logic to reason about stack-space usage, and modified the
verified CompCert C compiler to translate C level bound to x86 stack
bounds.  This quantitative logic is also based on the potential method
but has very rudimentary support for automation. It is not based on
efficient LP solving and cannot automatically derive symbolic
bounds.  In contrast, our main contribution is an automatic amortized
analysis for C that can derive parametric bounds for loops and
recursive functions fully automatically.
%
In this article, we also use a more general quantitative Hoare
logic that is parametric in the resource of interest.
